Factor Analysis on Report Citations, using a Combined Latent and logistic Model

### 2019-05-16 Manuscript for submission/manuscript.tex
Latest

@@

>>>>

One might wonder how traditional model selection methods, such as the Bayes Information Criterion (BIC;\cite{schwarz1978estimating}) or the AIC, where
\[
\mbox{BIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + |M| \log \frac{n(n-1)}{2},
\]
and
\[
\mbox{AIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + 2|M|,
\]

where $M$ is the current model,
$\mathbb{L}_n( \hat{\beta}(M))$ is the maximal log-likelihood for a given model $M$,
and $|M|$ is the number of free parameters in $M$, which is determined by the number of non-zeros in $S$ and the low-rank matrix $L$.
If rank$(L)=K$, we can establish the following
\[
|M| = \sum_{i < j}1_{\{S_{ij} > 0\}} + n K - \frac{K(K-1)}{2} + 1
\]
Because the number of free parameters in $L$ is $K$ plus $nk - K(K+1)/2$, which is the number of free parameters in determining $K$ orth-normal vectors. 
Additionally 1 in last is due to $\alpha$.
We want to find a M which minimizes BIC($M$) or AIC($M$) as a function of M. 
However these traditional methods seem to entail a serious problem. 
The assumptions used to derive BIC or AIC are not satisfied here, since each edges in a graph are not identically distributed.
Our experience shows that both BIC and AIC tend to choose the most parsimonious model with the smallest K and no ad-hoc dependency among all the estimated ($\hat{L}$,$\hat{S}$) with a pair of tuning parameters from given range of grid. 
We evaluate the model selected  
with following three evaluation metrics.
Table \ref{tab:table1}

@@

\begin{table}[h]
\centering
\begin{tabular}{c|ccc|ccc|ccc}
   & \multicolumn{3}{c|}{Case 1} & \multicolumn{3}{c|}{Case 2} & \multicolumn{3}{c}{Case 3} \\ \cline{2-10} 
   & SC        & AIC    & BIC    & SC        & AIC    & BIC    & SC        & AIC    & BIC   \\ \hline
M1 & 1         & 0      & 0      & 1         & 0      & 0      & 1         & 0      & 0     \\
M2 & 0.5       & 0      & 0      & 0.842     & 0      & 0      & 0.725     & 0      & 0     \\
M3 & 0.007     & 0      & 0      & 0.008     & 0      & 0      & 0.0113    & 0      & 0    
\end{tabular}
\caption{}
\label{tab:table1}
\end{table}
